Asteroseismology of GD358 with complex C/O core profiles

### 2016-03-16 msnew.tex
almost ready to go

\noindent where $n_{\rm obs}$ is the number of periods present in the pulsation spectrum and the weights $w_i$ are the inverse square of the uncertainties listed for each period in table \ref{gd}. We note that the two shortest period modes have 6000 times the weight of the longest period mode. Another way to think about this is to assume we have a calculated period that matches the highest period mode very poorly, being 20 seconds away. 20 seconds is roughly half the average period spacing for $\ell=1$ modes in the relevant area of parameter space and so it is the worse period fit one can get. In order to have the same impact on $\sigma_{\rm RMS}$, the lowest period mode would have to match to within 0.26 seconds. In essence this is almost ignoring the modes that have a period measurement uncertainty of 0.5~s or more. It is, however completely consistent with the relative uncertainty on the periods.

@@

With what we have discovered in section \ref{refinedfits}, it is only natural to be concerned about whether we have truly 
found a best fit. We performed a simple test to validate our fitting method, which consisted of using the exact same procedure 
to find a best fit to the periods of a model that was not on any of the grids we calculated, but that did have parameters that 
were very close to the best fit model. We used the period list for a model with parameters 
${\rm T_{eff}}=25570$~K, $M_*/M_\odot=0.5437$, $M_{\rm He}=-5.30$, $X_o=0.42$, and $q_{\rm fm}=0.175$, 
fixing $M_{\rm env}$ to -2.80, and including only the subset of 15 $\ell=1$ periods that match GD358's pulsation spectrum.

We first performed a fitting of the periods using the master (coarse) grid described in section \ref{grids}. This 
placed the best fit model in the appropriate region of parameter space. Then we refined our fits, using the grids 
described at the end of section \ref{periodspacing}. We are able to recover the best fit parameters adequately, with 
the top 10 best fit models having parameters 
${\rm T_{eff}}=25620 \pm 67$~K, $M_*/M_\odot=0.5431 \pm 0.0011$, $M_{\rm He}=-5.32 \pm 0.098$, $X_o=0.40$ for all top 
10 fits, and $q_{\rm fm}=0.175 \pm 0.5$. The top 10 best fits have \sigrms $\sim$ 0.5~s. We remind the reader that 
the step sizes in the second phase of the fitting are 20~K for ${\rm T_{eff}}$, 0.2 for $M_{\rm He}$, 0.2 for $X_o$, 
and 0.01 for $q_{\rm fm}$.

@@

We find a best fit effective temperature of 25,560~K for GD358, hotter than the recent spectroscopic determination of 24000~K \citep{Koester2013} by 2,000~K (4 sigmas). Our best fit model has a mass of 0.5438 \msun, a little over one sigma above the spectroscopic mass. For reasons discussed in section \ref{periodspacing}, while it is possible to determine whether a star is closer to the red edge or the blue edge of the instability strip, effective temperature is poorly constrained in asteroseismic fitting. As we can see from Fig. \ref{ffit3}, there are local minima that are almost as good as the global minimum we found, some at lower effective temperature. \emph{However}, the fact that the spectroscopic data point of \citet{Koester2013} falls far off the asymptotic period spacing trend (Fig. \ref{ffit2}, right panel) is a concern. This is a profound inconsistency that needs to be resolved.

@@

In this study, we varied the parameters that have traditionally been varied in this type of asteroseismic fitting, so that we can place our results side by side with other studies of DBVs, including KIC 8626021 \citep{Bischoff-Kim14}, EC200058 \citep{Bischoff-Kim11a}, and CBS114 \citep{Metcalfe05a}. We now have 4 DBVs that were the object of asteroseismic fitting that used a consistent set of models. Unfortunately, GD358 does not fit neatly into the trend (neither does EC20058). It is true, however that the two blue edge objects (EC20058 and KIC 8626021) have thinner helium layers ($M_{\rm He}=-6.10$ and $-7.90$ respectively) than the red edge stars ($M_{\rm He}=-5.40$ for GD358 and $-5.94$ for CBS114. Pinning down the proper effective temperature of each star is challenging. To be fully consistent, it is best to use the asteroseismic values, even if effective temperature is not strongly constrained asteroseimically. At best we can contrast blue edge versus red edge objects.

@@

%We have performed and published a preliminary fit of the star (Hawaii proceedings), where we found a temperature of 23,600 K, a mass of 0.605 $M_\odot$, \menv = -2.40, \mhe = -5.20, a central oxygen abundance of 0.99, and \qfm = 0.50. In the preliminary fits, the period list was not finalized and we did not include the 1065.260 s mode, because it was difficult to fit and we did not have a positive ell identification for the mode. It might be disheartening to observe such a big difference in the best fit parameters by just including or excluding one mode out of 15, but it is worth noting that the thickness of the pure helium layer was not affected much by the inclusion or exclusion of the 15th mode and refinements done in the search in this work. We emphasize again that in the final stages of our fitting for this work, we fixed the envelope mass to -2.80.
%
%In section \ref{periodspacing}, we discussed the degeneracy in the determination of the mass and effective temperature parameters. That degeneracy means that a unique determination of effective temperature and mass is not always possible.  The fits are also marginally sensitive to the central oxygen abundance. What is surprising is the big difference in the determination of the location of the edge of the homogeneous C/O core from our preliminary fits to the refined fits presented in this paper. If we take the best fit model from the preliminary work and include the 15th period when calculating the fitness number, the quality of the fit becomes significantly worse (2.84 s to 5.12 s). We would not expect a k=24 mode to be strongly trapped in the core, quite the contrary. This could be due to a core-envelope symmetry \citep{Montgomery03}, but more detailed studies would be required to make a more definitive statement. We should also keep in miind that the period lists used in the fits were close but not identical.

>>>>

\noindent where $n_{\rm obs}$ is the number of periods present in the pulsation spectrum and the weights $w_i$ are the inverse square of the uncertainties listed for each period in table \ref{gd}. We note that the two shortest period modes have 6000 times the weight of the longest period mode. Another way to think about this is to assume that we have a calculated period that matches the highest period mode very poorly, being 20 seconds away. 20 seconds is roughly half the average period spacing for $\ell=1$ modes in the relevant area of parameter space and so it is the worse period fit one can get. In order to have the same impact on $\sigma_{\rm RMS}$, the lowest period mode would have to match to within 0.26 seconds. In essence this is almost ignoring the modes that have a period measurement uncertainty of 0.5~s or more. It is, however completely consistent with the relative uncertainty on the periods and it provides us with a true measure of the goodness of fit, while accounting for all the data we have.

@@

With what we have discovered in section \ref{refinedfits}, it is only natural to be concerned about whether we have truly 
found a best fit. We performed a simple test to validate our fitting method, which consisted of using the exact same procedure 
to find a best fit to the periods of a model that was not on any of the grids we calculated, but that did have parameters that 
were very close to the best fit model. We used the period list for a model with parameters 
${\rm T_{eff}}=25630$~K, $M_*/M_\odot=0.57065$, \menv $=-2.05$ $M_{\rm He}=-5.55$, $X_o=0.52$, and $q_{\rm fm}=0.192$, including only the subset of 15 $\ell=1$ periods that match GD358's pulsation spectrum.

We first performed a fitting of the periods using the master (coarse) grid described in section \ref{grids}. This 
placed the best fit model in the appropriate region of parameter space. Then we refined our fits, using the grids 
described at the end of section \ref{periodspacing}. We are able to recover the best fit parameters adequately, with 
the all top 5 best fit models having parameters 
${\rm T_{eff}}=25000$~K, \mhe $=-2.1$, $M_{\rm env}=-5.5$, $X_o=0.50$, and $q_{\rm fm}=0.190$ and a mass ranging between  0.5730 and 0.5734 \msun. The best fit model has \sigrms $=0.31$~s. We remind the reader that 
the step sizes in the second phase of the fitting are 50~K for ${\rm T_{eff}}$, 0.0001 \msun for stellar mass, 0.1 for 0.1 for helium layer masses, 0.1 for $X_o$, and 0.005 for $q_{\rm fm}$.

@@

WE find a best fit effective temperature of 23,650~K and a mass of 0.5706 \msun for GD358. While the temperature is close to the recent spectroscopic determination of 24000~K \citep{Koester2013}, the mass is over one sigma above the spectroscopic mass. On the other hand, the mass matches almost exactly that found by \citet{Bergeron2011} (but the effective temperature is low). The fact that the spectroscopic data point of \citet{Koester2013} is far off the asymptotic period spacing trend (Fig. \ref{ffit2}, right panel) is a concern.

@@

In this study, we varied the parameters that have traditionally been varied in this type of asteroseismic fitting, so that we can place our results side by side with other studies of DBVs, including KIC 8626021 \citep{Bischoff-Kim14}, EC200058 \citep{Bischoff-Kim11a}, and CBS114 \citep{Metcalfe05a}. We now have 4 DBVs that were the object of asteroseismic fitting that used a consistent set of models. Among the 4, cooler best fit models do exhibit thicker pure helium envelopes. Pinning down the proper effective temperature of each star is challenging. To be fully consistent, it is best to use the asteroseismic values, even if effective temperature is not strongly constrained. We show the relationship between asteroseismic effective temperature and pure helium layer mass in Fig. \ref{ffit5}. Stellar mass also comes into play and ideally, we would like all 4 models to have the same mass. The models range in mass from 0.525 (Ec20058) to 0.640 \msun (CBS114). More detailed stellar evolution calculations would have to be performed in order to assess the significance of the trend observed with these 4 DBVs.

\begin{figure}
\epsscale{0.7}
\plotone{ffit5.eps}
%  \includegraphics[scale=0.70,viewport=50 0 50 350]{f2.png}
%  \includegraphics[width=0.9\columnwidth]{ffit3.eps}
\caption{
Relationship between effective temperature and pure helium layer mass in 4 DBVs fitted using similar models as GD358 in the present study. \label{ffit5}
}
\end{figure}

@@
